Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex
Motivation improved

Two different kinds of cloud approaches are available:
on the one hand, public facilities such as Amazon Web Services or 
Microsoft Azure allows users to chose a by default system configuration 
or to compose its own system features. On the other hand, institutions/companies 
are able to deploy their own cloud infrastructure by using software products 
like OpenStack.

>>>>

Two different kinds of cloud approaches are available:
on the one hand, public facilities such as Amazon Web Services or 
Microsoft Azure that allow users to chose a pre-configured system  
and on the other hand, institutions/companies 
are able to deploy their own cloud infrastructure by using software products 
like OpenStack.
